Unknown

### 2024-04-02 ms/ms.qmd
wrote methods for outlier removal from RH curves

library(readr)
# I am mostly putting placeholders here for objects/values that will need to be
# loaded eventually to use in paper.
fit_aa = read_rds("../objects/fit_dummy.rds")
dim_fit_aa = dim(fit_aa$fit)

@@

### Cleaning RH curves
n_rh_curve_raw = 2400 # export from adaptive-amphistomy/r/07_process-licor.R
n_points_per_rh_curves_raw = 100 # export from adaptive-amphistomy/r/07_process-licor.R
ca_min = 410 # export from adaptive-amphistomy/r/10_filter-rh-curves.R
ca_max = 420 # export from adaptive-amphistomy/r/10_filter-rh-curves.R
n_min_points_per_rh_curve = 10 # export from adaptive-amphistomy/r/10_filter-rh-curves.R

@@

WORKING HERE

>>>>

library(readr)
# I am mostly putting placeholders here for objects/values that will need to be
# loaded eventually to use in paper.
aa_args = read_rds("../objects/aa_args.rds")
fit_aa = read_rds("../objects/fit_dummy.rds")
dim_fit_aa = dim(fit_aa$fit)

@@

### Cleaning RH curves
n_rh_curve_raw = 2400 # export from adaptive-amphistomy/r/07_process-licor.R
n_points_per_rh_curves_raw = 100 # export from adaptive-amphistomy/r/07_process-licor.R
ca_min = aa_args$ca_min
ca_max = aa_args$ca_max
n_min_points_per_rh_curve = aa_args$n_min_points_per_rh_curve
outlier_threshold = aa_args$outlier_threshold

@@

#### Remove outliers within each \agcurve{} curve

*Rationale*: Individual outliers within \agcurve{} curves, usually caused by transitory changes in chamber conditions, exert undue leverage on parameter estimates and cause bias and/or low precision in parameter estimates.

*Procedure*: We fit provisional quadratic regressions for each curve using ordinary least squares with the `lm()` function in *R*. We sequentially removed data points with an external studentized residual greater than `r outlier_threshold` until none remained.

were likely due to measurement error or leaf damage.
WORKING HERE
